### 2020-01-17 thesis_template/2_RelatedWork/relatedWork.tex
added

Figure 2-8 and 2-9 represent the result of the experiments. For both data structures, integer elements addition shows the fastest runtime among all object types. 
This is because the compilers know each integer need 4 bytes to be stored in memory so that the space for memory that should be allocated is easily inspected. 
The elements addition of strings and array of character behave similally among each languages. These two types of elements addition perform the similar speed and significantly slower than integer addition. 
Customer object addition is the slowest in Java and seems to have little impact of initialization of size of ArrayList. However, in Rust the addition of Customer object is the second fastest among all element typs.

@@

>>>>

Figure 2-10, 2-11, 2-12, and 2-13 represent the result of the experiments. For both data structures, integer elements addition shows the fastest runtime among all object types. 
This is because the compilers know each integer need 4 bytes to be stored in memory so that the space for memory that should be allocated is easily inspected. 
For the same reason, the initialization of data structures whose elements are integers alaways improves runtim performance.

The elements addition of strings and array of character behave similally among each languages. These two types of elements addition perform the similar speed and significantly slower than integer addition. 
Customer object addition is the slowest in Java. However, in Rust the addition of Customer object is the second fastest among all element typs.
The impacts of initialization of Java ArrayList vary among elemet types. On the other hand, the initailization Rust Vector always improves runtime performance for any of 4 types of elements addition.

@@

\begin{figure}[htb]
    \includegraphics[width=15cm]{java_arraylist_difference.eps}
    \caption{Difference of Memory allocation of Java ArrayList between Non-initialization and Initialization}
    \label{fig:Sampling}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_arraylist_difference.eps}
    \caption{Difference of Memory allocation of Rust Vector between Non-initialization and Initialization}
    \label{fig:Sampling}
\end{figure}
